PLAE enables quick and easy searching across one million ocular transcriptomes

### 2022-07-14 manuscript_00.Rmd
updates

Cell type marker genes can be proposed on the basis of existing knowledge about their function and/or based on high expression differences when comparing to other cell types. We can further narrow down the list of markers by using the  diersity of studies and organisms in scEiaD. We first identify a set of "well supported" cell types which we define as cell types which have two or more independent studies across both human and mouse (`r supTab_cap(name = 'well_supported_celltypes_tab', display = 'cite')`). These

>>>>

Cell type marker genes can be proposed on the basis of existing knowledge about their function and/or based on high expression differences when comparing to other cell types. We can further narrow down the list of markers by using the  diversity of studies and organisms in scEiaD to propose a set of community supported cell type markers. We first identify a set of well supported cell types which we define as cell types which have two or more independent studies across both human and mouse (`r supTab_cap(name = 'well_supported_celltypes_tab', display = 'cite')`). These cell types were then assessed to identify differentially expressed genes which met the following criteria: 1. padj less than $1 x 10^-4
in both human and mouse, 2. mean log2 fold change greater than two, and 3. mean padj less than $1 x 10^-5
